---
title: "PlotFix"
author: "Rangga"
date: "2022-07-27"
output: 
  html_document:
    css: bootstrap.min.css
---


```{r setup, include=FALSE}
# clear-up the environment
rm(list = ls())

# chunk options
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  fig.align = "center",
  comment = "#>"
)

# scientific notation
options(scipen = 9999)
```

#Library

```{r}
library(tidyverse)
library(scales)
library(ggthemes)
library(gridExtra)
library(ggfx)
library(extrafont)
library(scales)
library(lubridate)
```

#Read Data

```{r}
bgdata <- read.csv("datainput/bgg_db_1806.csv")
head(bgdata)
```

# Trend and Popularity

## Number of Games Released

```{r}
#Prepare the Data
bgdata$year <- as.character(bgdata$year)

bgtrend <-
bgdata %>% 
  select(names,year) %>% 
  filter(year >= 1955, year <= 2017) %>% 
  group_by(year) %>% 
  summarise(count = n()) %>% 
  ungroup()
```

```{r}
#Plot Code
ggplot(bgtrend, aes(year, count))+
    with_outer_glow(geom_line(aes(group=1),color = "#CAB0B9"), colour = "#F21F66", sigma = 10, expand = 0.7)+ 
    with_outer_glow(geom_point(color = "#CAB0B9"), colour = "#F21F66", sigma = 10, expand = 0.7)+ 
    scale_x_discrete(breaks = seq(1957,2017,5))+ 
    scale_y_continuous(breaks = seq(0,420,60))+ 
    labs(x = "Year",
         y = NULL,
         title = "Trend by Games Released per Year")+ 
    theme(plot.background = element_rect(fill = "#231F20", color = "#231F20"),
        panel.background = element_rect(fill = "#231F20"),
        panel.grid = element_line(alpha(colour = "#525252",alpha = 0.2)),
        plot.title = element_text(colour = "#FDF202",face = "bold", family = "Copperplate Gothic Bold"),
        plot.subtitle = element_text(colour = "#F2F2F2", face = "italic", size = 10),
        axis.title.x = element_text(colour = "#FDF202",family = "OCR A Extended", face = "bold"),
        axis.text.x = element_text(color = "White", family = "OCR A Extended", face = "bold"),
        axis.text.y = element_text(color = "White", face = "italic", family = "OCR A Extended"))
```

## Most Popular Games

```{r}
#Prepare the Data
bgpopular <-
bgdata %>% 
  select(names,owned) %>% 
  group_by(names) %>% 
  summarise(total = sum(owned)) %>%
  ungroup() %>% 
  top_n(10)
```

```{r}
#Plot Code
ggplot(bgpopular, aes(reorder(names,total), total)) +
  with_outer_glow(geom_segment(aes(x = reorder(names,total), 
                                   xend = reorder(names,total), 
                                   y = 0, 
                                   yend = total), color = "#C4FEFE", size = 0.5),colour = "#00F0FF") +
  with_outer_glow(geom_point(color = "#CAB0B9", size = 1),colour = "#F21F66#ECD203")+
  coord_flip()+
  scale_y_continuous(breaks = seq(0,112000,22400),
                     labels = comma)+
  labs(x = NULL,
       y = "Total Owned",
       title = "Most Popular Games",
       subtitle = "by num. of Owned")+
  theme(plot.background = element_rect(fill = "#231F20", color = "#231F20"),
        panel.background = element_rect(fill = "#231F20"),
        panel.grid = element_line(alpha(colour = "#231F20")),
        plot.title = element_text(colour = "#FDF202",face = "bold", family = "Copperplate Gothic Bold"),
        plot.subtitle = element_text(colour = "#F2F2F2", face = "italic", size = 10),
        axis.title.x = element_text(colour = "#FDF202", family = "OCR A Extended", face = "bold"),
        axis.text.x = element_text(color = "White", family = "OCR A Extended", face = "italic"),
        axis.text.y = element_text(color = "White", face = "italic", family = "OCR A Extended"))
```

## Most Rated Games

```{r}
#Prepare the Data
bgvotes <-
bgdata %>% 
  select(names,num_votes) %>% 
  group_by(names) %>% 
  summarise(total = sum(num_votes)) %>%
  ungroup() %>% 
  top_n(10)
```

```{r}
#Plot Code
ggplot(bgvotes, aes(reorder(names,total), total)) +
  with_outer_glow(geom_segment(aes(x = reorder(names,total), 
                                   xend = reorder(names,total), 
                                   y = 0, 
                                   yend = total), color = "#C4FEFE", size = 0.5),colour = "#00F0FF") +
  with_outer_glow(geom_point(color = "#CAB0B9", size = 1),colour = "#F21F66#ECD203")+
  coord_flip()+
  scale_y_continuous(breaks = seq(0,80000,20000),
                     labels = comma)+
  labs(x = NULL,
       y = "Total Votes",
       title = "Most Rated Games",
       subtitle = "by num. of Votes")+
  theme(plot.background = element_rect(fill = "#231F20", color = "#231F20"),
        panel.background = element_rect(fill = "#231F20"),
        panel.grid = element_line(alpha(colour = "#231F20")),
        plot.title = element_text(colour = "#FDF202",face = "bold", family = "Copperplate Gothic Bold"),
        plot.subtitle = element_text(colour = "#F2F2F2", face = "italic", size = 10),
        axis.title.x = element_text(colour = "#FDF202", family = "OCR A Extended", face = "bold"),
        axis.text.x = element_text(color = "White", family = "OCR A Extended", face = "italic"),
        axis.text.y = element_text(color = "White", face = "italic", family = "OCR A Extended"))
```

#Rating Explanation

##Rating Distribution

```{r}
#Prepare the Data
rating <- 
  bgdata %>% 
  select(avg_rating,geek_rating) %>% 
  gather(rating) %>% 
  mutate(rating = as.factor(rating))
```

```{r}
#Plot Code
ggplot(rating,aes(x=value, col = rating)) + 
  with_outer_glow(geom_density(data = .%>% filter( rating == "avg_rating"),
                               alpha=0,fill = "#231F20",size=0.4),colour="#FDF202",
                  sigma = 10,expand = 0.7)+
  with_outer_glow(geom_density(data = .%>% filter( rating == "geek_rating"),
                               alpha=0,fill = "#231F20",size=0.4),colour="#00F0FF",
                  sigma = 10,expand = 0.7)+
  scale_x_continuous(breaks = seq(3,9,1))+
  scale_color_manual(values = c("#FCFFBE", "#C4FEFE"),
                     labels=c('Avg. Rating', 'Geek Rating'))+
  labs(x= "Rating",
       y= "",
       title = "Average Rating VS Geek Rating")+
  theme(legend.position="top",legend.direction="horizontal",
        legend.background = element_rect(fill="#231F20", color = "#231F20"),
        legend.key = element_rect(fill="#231F20", color = "#231F20"),
        legend.title = element_text(colour = "#231F20", face ="bold", size = 9),
        legend.text = element_text(color="White", face ="italic"),
        legend.key.size= unit(0.4, 'cm'),
        plot.background = element_rect(fill = "#231F20", color = "#231F20"),
        panel.background = element_rect(fill = "#231F20"),
        panel.grid = element_line(alpha(colour = "#525252",alpha = 0.2)),
        panel.grid.major.x = element_line(colour ="#231F20"),
        panel.grid.minor.x = element_line(colour ="#231F20"),
        plot.title = element_text(colour = "#FDF202",face = "bold", family="Copperplate Gothic Bold"),
        axis.title.x = element_text(colour = "#FDF202",family="OCR A Extended",face="bold"),
        axis.text.x=element_text(color="White",family="OCR A Extended", face="italic"),
        axis.text.y=element_text(color="White", face="italic", family = "OCR A Extended"))
```

## Geek Rating (Votes vs Owned)

```{r}
#Prepare the Data
gq0 <- quantile(bgdata$geek_rating)[1] #Get each quantiles
gq25 <- quantile(bgdata$geek_rating)[2]
gq50 <- quantile(bgdata$geek_rating)[3]
gq75 <- quantile(bgdata$geek_rating)[4]
gq100 <- quantile(bgdata$geek_rating)[5]

#Create a function
convert_ratings = function(x){
  if(x <= gq25) {x <- "0-25%"}
  else if(x <= gq50) {x <- "25-50%"}
  else if(x <= gq75) {x <- "50-75%"}
  else {x <- "75-100%"}
}

bgdata$geek_group <- sapply(X = bgdata$geek_rating, 
                            FUN = convert_ratings)
geek.group <- bgdata[,c("num_votes","owned","geek_group")]
```

```{r}
#Plot Code
ggplot(geek.group,aes(log(owned),log(num_votes), col=geek_group))+
  with_bloom(geom_point(alpha=0.8),strength = 2)+
  scale_color_manual(values = c("#00F0FF","#EF3524","#FDF202","#F16393"))+
  labs(x= "Owned",
       y= "Votes",
       title = "Owned VS Num. of Votes",
       subtitle = "Relationship by Geek Rating Groups Quantiles",
       col = "Geek Quantiles:")+
  theme(legend.position="right",legend.direction="vertical",
        legend.background = element_rect(fill="#231F20", color = "#231F20"),
        legend.key = element_rect(fill="#231F20", color = "#231F20"),
        legend.title = element_text(colour = "#FDF202", face ="bold", size = 9),
        legend.text = element_text(color="White", face ="italic", family="OCR A Extended"),
        plot.background = element_rect(fill = "#231F20", color = "#231F20"),
        legend.key.size= unit(0.3, 'cm'),
        panel.background = element_rect(fill = "#231F20"),
        panel.grid = element_line(alpha(colour = "#525252",alpha = 0.2)),
        panel.grid.minor.x = element_line(colour ="#231F20"),
        plot.title = element_text(colour = "#FDF202",face = "bold", family="Copperplate Gothic Bold"),
        plot.subtitle = element_text(colour = "#F2F2F2", face = "italic", size = 10),
        axis.title.x = element_text(colour = "#FDF202",family="OCR A Extended",face="bold"),
        axis.title.y = element_text(colour = "#FDF202",family="OCR A Extended",face="bold"),
        axis.text.x=element_text(color="White",family="OCR A Extended", face="italic"),
        axis.text.y=element_text(color="White", face="italic", family = "OCR A Extended"))
```

## Average Rating (Votes vs Owned)

```{r}
#Prepare the Data
aq0 <- quantile(bgdata$avg_rating)[1] #Get each Quantiles
aq25 <- quantile(bgdata$avg_rating)[2]
aq50 <- quantile(bgdata$avg_rating)[3]
aq75 <- quantile(bgdata$avg_rating)[4]
aq100 <- quantile(bgdata$avg_rating)[5]

#Create a function
convert_ratings = function(x){
  if(x <= aq25) {x <- "0-25%"}
  else if(x <= aq50) {x <- "25-50%"}
  else if(x <= aq75) {x <- "50-75%"}
  else {x <- "75-100%"}
}

bgdata$avg_group <- sapply(X = bgdata$avg_rating, 
                            FUN = convert_ratings)
avg.group <- bgdata[,c("num_votes","owned","avg_group")]
```

```{r}
ggplot(avg.group,aes(log(owned),log(num_votes), col=avg_group))+
  with_bloom(geom_point(alpha=0.8),strength = 2)+
  scale_color_manual(values = c("#00F0FF","#EF3524","#FDF202","#F16393"))+
  labs(x= "Owned",
       y= "Votes",
       title = "Owned VS Num. of Votes",
       subtitle = "Relationship by Average Rating Groups Quantiles",
       col = "Average Quantiles:")+
  theme(legend.position="right",legend.direction="vertical",
        legend.background = element_rect(fill="#231F20", color = "#231F20"),
        legend.key = element_rect(fill="#231F20", color = "#231F20"),
        legend.title = element_text(colour = "#FDF202", face ="bold", size = 9),
        legend.text = element_text(color="White", face ="italic", family="OCR A Extended"),
        plot.background = element_rect(fill = "#231F20", color = "#231F20"),
        legend.key.size= unit(0.3, 'cm'),
        panel.background = element_rect(fill = "#231F20"),
        panel.grid = element_line(alpha(colour = "#525252",alpha = 0.2)),
        panel.grid.minor.x = element_line(colour ="#231F20"),
        plot.title = element_text(colour = "#FDF202",face = "bold", family="Copperplate Gothic Bold"),
        plot.subtitle = element_text(colour = "#F2F2F2", face = "italic", size = 10),
        axis.title.x = element_text(colour = "#FDF202",family="OCR A Extended",face="bold"),
        axis.title.y = element_text(colour = "#FDF202",family="OCR A Extended",face="bold"),
        axis.text.x=element_text(color="White",family="OCR A Extended", face="italic"),
        axis.text.y=element_text(color="White", face="italic", family = "OCR A Extended"))
```

# Games Category & Mechanics

```{r}
#Prepare the Data
game_cat<-as.data.frame(table(str_trim(unlist(strsplit(str_trim(as.character(bgdata$category)), ", ")))))
game_mec<-as.data.frame(table(str_trim(unlist(strsplit(str_trim(as.character(bgdata$mechanic)), ", ")))))

top5_cat <- game_cat[order(game_cat$Freq, decreasing=T)[1:5],]
top5_mec <- game_mec[order(game_mec$Freq, decreasing=T)[1:5],]

top5_cat$fraction <- round((top5_cat$Freq / sum(top5_cat$Freq))*100)
top5_cat$fraction <- sub("$", "%", top5_cat$fraction)

hsizec <- 2
top5_cat <- top5_cat %>% 
  mutate(x = hsizec)

top5_mec$fraction <- round((top5_mec$Freq / sum(top5_mec$Freq))*100)
top5_mec$fraction <- sub("$", "%", top5_mec$fraction)

hsizem <- 2
top5_mec <- top5_mec %>% 
  mutate(x = hsizem)
```

## Top 5 Categories

```{r}
#Plot Code
ggplot(top5_cat, aes(x = hsizec, y = Freq, fill = Var1, col = Var1)) +
  with_bloom(geom_col(fill="#231F20"),sigma = 15, strength=2) +
  with_bloom(geom_text(aes(label = fraction),
            color = "#F2F2F2",
            position = position_stack(vjust = 0.5),family = "OCR A Extended")) +
  guides(fill = "none") + 
  labs(x=NULL,
       y=NULL,
       title = "Top 5 Categories",
       subtitle = "by Total Games",
       col = "Categories:")+
  scale_color_manual(values = c("#00F0FF","#FF003C","#FDF202","#EF3524","#D039DD"))+
  scale_fill_manual(values = c("#231F20","#231F20","#231F20","#231F20","#231F20"))+
  xlim(c(0.2, hsizec + 0.5)) +
  coord_polar(theta = "y") +
  theme(legend.position="right",legend.direction="vertical",
        legend.background = element_rect(fill="#231F20", color = "#231F20"),
        legend.key = element_rect(fill="#231F20", color = "#231F20"),
        legend.title = element_text(colour = "#FDF202", face ="bold", size = 9),
        legend.text = element_text(color="White", face ="italic", family="Times New Roman"),
        legend.key.size= unit(0.3, 'cm'),
        plot.background = element_rect(fill="#231F20"),
        panel.background = element_rect(fill = "#231F20"),
        panel.grid = element_line(colour = "#231F20"),
        plot.title = element_text(colour = "#FDF202",face = "bold", family="Copperplate Gothic Bold"),
        plot.subtitle = element_text(colour = "#F2F2F2", face = "italic", size = 10),
        axis.text.x=element_text(color="#231F20"),
        axis.text.y=element_text(color="#231F20"))
```

## Top 5 Mechanics

```{r}
#Plot Code
ggplot(top5_mec, aes(x = hsizem, y = Freq, fill = Var1, col = Var1)) +
  with_bloom(geom_col(fill="#231F20"),sigma = 15, strength=2) +
  with_bloom(geom_text(aes(label = fraction),
            color = "#F2F2F2",
            position = position_stack(vjust = 0.5),
            family = "OCR A Extended")) +
  guides(fill = "none") + 
  labs(x=NULL,
       y=NULL,
       title = "Top 5 Mechanics",
       subtitle = "by Total Games",
       col = "Categories:")+
  scale_color_manual(values = c("#00F0FF","#FF003C","#FDF202","#EF3524","#D039DD"))+
  scale_fill_manual(values = c("#231F20","#231F20","#231F20","#231F20","#231F20"))+
  xlim(c(0.2, hsizem + 0.5)) +
  coord_polar(theta = "y") +
  theme(legend.position="right",legend.direction="vertical",
        legend.background = element_rect(fill="#231F20", color = "#231F20"),
        legend.key = element_rect(fill="#231F20", color = "#231F20"),
        legend.title = element_text(colour = "#FDF202", face ="bold", size = 9),
        legend.text = element_text(color="White", face ="italic", family="Times New Roman"),
        legend.key.size= unit(0.3, 'cm'),
        plot.background = element_rect(fill="#231F20"),
        panel.background = element_rect(fill = "#231F20"),
        panel.grid = element_line(colour = "#231F20"),
        plot.title = element_text(colour = "#FDF202",face = "bold", family="Copperplate Gothic Bold"),
        plot.subtitle = element_text(colour = "#F2F2F2", face = "italic", size = 10),
        axis.text.x=element_text(color="#231F20"),
        axis.text.y=element_text(color="#231F20"))
```

#Players

## Games with most Max Players Allowed
```{r}
bgdata %>% 
  select(names,max_players) %>% 
  group_by(names) %>%
  ungroup() %>% 
  top_n(1)
```

## Age Distribution

```{r}
#Prepare the Data
age.dist <- 
  bgdata %>% 
  select(age) %>% 
  filter(age <= 30)
```

```{r}
ggplot(age.dist, aes(x=age))+
  with_outer_glow(geom_density(color = "#C4FEFE"),colour = "#00F0FF",sigma = 10,expand = 0.7)+
    scale_x_continuous(breaks = seq(0,20,4))+
    labs(x= "Age",
         y= NULL,
         title = "Age Distribution")+
    theme(plot.background = element_rect(fill = "#231F20", color = "#231F20"),
        panel.background = element_rect(fill = "#231F20"),
        panel.grid = element_line(alpha(colour = "#525252",alpha = 0.2)),
        panel.grid.major.x = element_line(colour ="#231F20"),
        panel.grid.minor.x = element_line(colour ="#231F20"),
        plot.title = element_text(colour = "#FDF202",face = "bold", family="Copperplate Gothic Bold"),
        plot.subtitle = element_text(colour = "#F2F2F2", face = "italic", size = 10),
        axis.title.x = element_text(colour = "#FDF202",family="OCR A Extended",face="bold"),
        axis.text.x=element_text(color="White",family="OCR A Extended", face="italic"),
        axis.text.y=element_text(color="White", face="italic", family = "OCR A Extended"))
```

## Rating by Group of Age

```{r}
#Prepare the Data
convert_ages = function(x){
  if(x <= 5) {x <- "0-5"}
  else if(x > 5 & x <= 10) {x <- "6-10"}
  else if(x > 10 & x <= 15) {x <- "11-15"}
  else if(x > 15 & x <= 20) {x <- "16-20"}
  else {x <- "21+"}
}

bgdata$age_group <- sapply(X = bgdata$age, 
                            FUN = convert_ages)
age.rating <- bgdata %>% select(age_group,avg_rating)
dataMedian <- summarise(group_by(age.rating, age_group), rating_med = median(avg_rating))
dataMedian$rating_med <- round(dataMedian$rating_med,2)
```

```{r}
#Plot Code
ggplot(age.rating,aes(age_group,avg_rating, col=age_group))+
  with_bloom(geom_boxplot(fill="#231F20"),sigma=15,strength = 2)+
  geom_text(data = dataMedian, aes(age_group, rating_med, label=rating_med),
            family = "OCR A Extended",
            position = position_dodge(width = 0.8), size = 3, vjust = -0.5)+
  scale_color_manual(breaks = c("0-5", "6-10", "11-15","16-20","21+"),
                     values = c("#00F0FF","#FF003C","#FDF202","#EF3524","#D039DD"))+
  scale_fill_manual(values = c("#231F20","#231F20","#231F20","#231F20","#231F20"))+
  scale_x_discrete(limits = c("0-5", "6-10", "11-15","16-20","21+"))+
  labs(x= "Age",
       y= "Rating",
       title = "Rating vs Age",
       subtitle = "average Rating per Group of Age",
       col = "Age Groups:")+
  theme(legend.position="right",legend.direction="vertical",
        legend.background = element_rect(fill="#231F20", color = "#231F20"),
        legend.key = element_rect(fill="#231F20", color = "#231F20"),
        legend.title = element_text(colour = "#FDF202", face ="bold", size = 9),
        legend.text = element_text(color="White", face ="italic", family="OCR A Extended"),
        legend.key.size= unit(0.5, 'cm'),
        plot.background = element_rect(fill = "#231F20", color = "#231F20"),
        panel.background = element_rect(fill = "#231F20"),
        panel.grid = element_line(alpha(colour = "#231F20",alpha = 0.2)),
        panel.grid.major.x = element_line(colour ="#231F20"),
        panel.grid.minor.x = element_line(colour ="#231F20"),
        plot.title = element_text(colour = "#FDF202",face = "bold", family="Copperplate Gothic Bold"),
        plot.subtitle = element_text(colour = "#F2F2F2", face = "italic", size = 10),
        axis.title.x = element_text(colour = "#FDF202",family="OCR A Extended",face="bold"),
        axis.title.y = element_text(colour = "#FDF202",family="OCR A Extended",face="bold"),
        axis.text.x=element_text(color="White",family="OCR A Extended", face="italic"),
        axis.text.y=element_text(color="White", face="italic", family = "OCR A Extended"))
```
## Votes and Owned Relationship by Age

```{r}
#Plot Code
age.rating.o <- bgdata[,c("age_group","owned","num_votes","avg_rating")]
ggplot(age.rating.o,aes(log(num_votes),log(owned), col=age_group))+
  with_bloom(geom_point(alpha=0.8),strength = 3)+
  scale_color_manual(breaks = c("0-5", "6-10", "11-15","16-20","21+"),
                     values = c("#00F0FF","#FF003C","#FDF202","#EF3524","#D039DD"))+
  labs(x= "Owned",
       y= "Votes",
       title = "Owned VS Num. of Votes",
       subtitle = "Relationship by average Rating Groups Quantiles",
       col = "Avg. Quantiles:")+
  theme(legend.position="right",legend.direction="vertical",
        legend.background = element_rect(fill="#231F20", color = "#231F20"),
        legend.key = element_rect(fill="#231F20", color = "#231F20"),
        legend.title = element_text(colour = "#FDF202", face ="bold", size = 9),
        legend.text = element_text(color="White", face ="italic", family="OCR A Extended"),
        legend.key.size= unit(0.3, 'cm'),
        plot.background = element_rect(fill = "#231F20", color = "#231F20"),
        panel.background = element_rect(fill = "#231F20"),
        panel.grid = element_line(alpha(colour = "#525252",alpha = 0.2)),
        panel.grid.minor.x = element_line(colour ="#231F20"),
        plot.title = element_text(colour = "#FDF202",face = "bold", family="Copperplate Gothic Bold"),
        plot.subtitle = element_text(colour = "#F2F2F2", face = "italic", size = 10),
        axis.title.x = element_text(colour = "#FDF202",family="OCR A Extended",face="bold"),
        axis.title.y = element_text(colour = "#FDF202",family="OCR A Extended",face="bold"),
        axis.text.x=element_text(color="White",family="OCR A Extended", face="italic"),
        axis.text.y=element_text(color="White", face="italic", family = "OCR A Extended"))
```

#Meet your Maker

## Designer with Most Games

```{r}
#Prepare the Data
bgdesigner <- 
bgdata %>%
    filter(!designer %in% c('none', '(Uncredited)')) %>%
    group_by(designer) %>%
    summarize(count=n()) %>%
    arrange(-count) %>%
    ungroup() %>% 
    top_n(10,count)
```

```{r}
#Plot Code
ggplot(bgdesigner, aes(reorder(designer, count), count, col = count)) + 
    with_bloom(geom_bar(stat='identity', fill='#231F20', width=0.8),sigma = 15, strength=2) +
    scale_color_gradient(low="#FDF202", high = "#EF3524") +
    scale_y_continuous(breaks = seq(0,150,15))+
    coord_flip()+
    labs(x= NULL,
         y= "Total",
         title = "Designer",
         subtitle = "by Games created.")+
    theme(legend.position="none",
          plot.background = element_rect(fill = "#231F20", color = "#231F20"),
          panel.background = element_rect(fill = "#231F20"),
          panel.grid = element_line(alpha(colour = "#231F20")),
          plot.title = element_text(colour = "#FDF202",face = "bold", family="Copperplate Gothic Bold"),
          plot.subtitle = element_text(colour = "#F2F2F2", face = "italic", size = 10),
          axis.title.x = element_text(colour = "#FDF202",family="OCR A Extended",face="bold"),
          axis.text.x=element_text(color="White",family="OCR A Extended"),
          axis.text.y=element_text(color="White", face="italic", family = "OCR A Extended"))
```

## Designer with Most Popular Games.

```{r}
#Prepare the Data
bgdesigner.pop <- 
    bgdata %>%
    filter(!designer %in% c('none', '(Uncredited)')) %>%
    group_by(designer) %>%
    summarize(count=n(), owned=sum(owned)) %>%
    filter(count >= 5) %>%
    arrange(-owned) %>%
    ungroup() %>% 
    top_n(10)
```

```{r}
#Plot Code
ggplot(bgdesigner.pop, aes(reorder(designer, owned), owned, col = owned)) + 
    with_bloom(geom_bar(stat='identity', fill='#231F20', width=0.8),sigma = 15, strength=2) +
    scale_color_gradient(low="#FDF202", high = "#EF3524") +
    scale_y_continuous(breaks = seq(0,4e5,5e4),
                       labels = comma)+
    coord_flip()+
    labs(x= NULL,
         y= "Total",
         title = "Designer",
         subtitle = "by Games owned.")+
    theme(legend.position="none",
          plot.background = element_rect(fill = "#231F20", color = "#231F20"),
          panel.background = element_rect(fill = "#231F20"),
          panel.grid = element_line(alpha(colour = "#231F20")),
          plot.title = element_text(colour = "#FDF202",face = "bold", family="Copperplate Gothic Bold"),
          plot.subtitle = element_text(colour = "#F2F2F2", face = "italic", size = 10),
          axis.title.x = element_text(colour = "#FDF202",family="OCR A Extended",face="bold"),
          axis.text.x=element_text(color="White",family="OCR A Extended", angle = 15),
          axis.text.y=element_text(color="White", face="italic", family = "OCR A Extended"))
```

# Complexity

## Relationship between Weight and Max Times

```{r}
#Prepare the Data
convert_weight = function(x){
  if(x <= 1) {x <- "1"}
  else if(x <= 2) {x <- "2"}
  else if(x <= 3) {x <- "3"}
  else if(x <= 4) {x <- "4"}
  else {x <- "5"}
}

bgdata$weight_group <- sapply(X = bgdata$weight, 
                            FUN = convert_weight)
```

```{r}
#Plot Code
ggplot(bgdata,aes(weight,log(max_time), col=weight_group))+
  with_bloom(geom_boxplot(fill="#231F20"),sigma=5,strength = 2)+
  scale_color_manual(breaks = c("1", "2", "3", "4", "5"),
                     values = c("#FDF202","#FF003C","#00F0FF","#EF3524","#D039DD"))+
  scale_fill_manual(values = c("#231F20","#231F20","#231F20","#231F20","#231F20"))+
  labs(x= "Weight",
       y= "Log. Max Time",
       title = "Weight vs Max Time",
       subtitle = "Complexity by Max Time",
       col = "Weights:")+
  theme(legend.position="right",legend.direction="vertical",
        legend.background = element_rect(fill="#231F20", color = "#231F20"),
        legend.key = element_rect(fill="#231F20", color = "#231F20"),
        legend.title = element_text(colour = "#FDF202", face ="bold", size = 9),
        legend.text = element_text(color="White", face ="italic", family="OCR A Extended"),
        legend.key.size= unit(0.5, 'cm'),
        plot.background = element_rect(fill = "#231F20", color = "#231F20"),
        panel.background = element_rect(fill = "#231F20"),
        panel.grid = element_line(alpha(colour = "#231F20",alpha = 0.2)),
        panel.grid.major.x = element_line(colour ="#231F20"),
        panel.grid.minor.x = element_line(colour ="#231F20"),
        plot.title = element_text(colour = "#FDF202",face = "bold", family="Copperplate Gothic Bold"),
        plot.subtitle = element_text(colour = "#F2F2F2", face = "italic", size = 10),
        axis.title.x = element_text(colour = "#FDF202",family="OCR A Extended",face="bold"),
        axis.title.y = element_text(colour = "#FDF202",family="OCR A Extended",face="bold"),
        axis.text.x=element_text(color="White",family="OCR A Extended", face="italic"),
        axis.text.y=element_text(color="White", face="italic", family = "OCR A Extended"))
```

## Relationship between Weight and Age Group

```{r}
#Plot Code
ggplot(bgdata, aes(x=age_group,weight,col=weight_group)) +
  with_bloom(geom_jitter( size=0.7),strength = 1)+
  scale_color_manual(breaks = c("1", "2", "3", "4", "5"),
                     values = c("#FDF202","#FF003C","#00F0FF","#EF3524","#D039DD"))+
  scale_x_discrete(limits = c("0-5", "6-10", "11-15","16-20","21+"))+
  labs(x= "Age",
       y= "Weight",
       title = "Weight vs Age Group",
       subtitle = "Relationship between Weight and Age Group",
       col = "Weights:")+
  theme(legend.position="right",legend.direction="vertical",
        legend.background = element_rect(fill="#231F20", color = "#231F20"),
        legend.key = element_rect(fill="#231F20", color = "#231F20"),
        legend.title = element_text(colour = "#FDF202", face ="bold", size = 9),
        legend.text = element_text(color="White", face ="italic", family="OCR A Extended"),
        plot.background = element_rect(fill = "#231F20", color = "#231F20"),
        panel.background = element_rect(fill = "#231F20"),
        panel.grid = element_line(alpha(colour = "#231F20",alpha = 0.2)),
        panel.grid.minor.x = element_line(colour ="#231F20"),
        plot.title = element_text(colour = "#FDF202",face = "bold", family="Copperplate Gothic Bold"),
        plot.subtitle = element_text(colour = "#F2F2F2", face = "italic", size = 10),
        axis.title.x = element_text(colour = "#FDF202",family="OCR A Extended",face="bold"),
        axis.title.y = element_text(colour = "#FDF202",family="OCR A Extended",face="bold"),
        axis.text.x=element_text(color="White",family="OCR A Extended", face="italic"),
        axis.text.y=element_text(color="White", face="italic", family = "OCR A Extended"))
```

## Relationship between Weight and Rating Group

```{r}
#Plot Code
ggplot(bgdata, aes(weight,geek_group,col=weight_group)) +
  with_bloom(geom_jitter( size=0.7),strength = 1)+
  scale_color_manual(breaks = c("1", "2", "3","4","5"),
                     values = c("#FDF202","#FF003C","#00F0FF","#EF3524","#D039DD"))+
  scale_x_discrete(limits = c("0-5", "6-10", "11-15","16-20","21+"))+
  labs(x= "Weight",
       y= "Rating",
       title = "Rating vs Weight Group",
       subtitle = "Relationship between Rating and Weight Group",
       col = "Weights:")+
  theme(legend.position="right",legend.direction="vertical",
        legend.background = element_rect(fill="#231F20", color = "#231F20"),
        legend.key = element_rect(fill="#231F20", color = "#231F20"),
        legend.title = element_text(colour = "#FDF202", face ="bold", size = 9),
        legend.text = element_text(color="White", face ="italic", family="OCR A Extended"),
        plot.background = element_rect(fill = "#231F20", color = "#231F20"),
        panel.background = element_rect(fill = "#231F20"),
        panel.grid = element_line(alpha(colour = "#231F20",alpha = 0.2)),
        panel.grid.minor.x = element_line(colour ="#231F20"),
        plot.title = element_text(colour = "#FDF202",face = "bold", family="Copperplate Gothic Bold"),
        plot.subtitle = element_text(colour = "#F2F2F2", face = "italic", size = 10),
        axis.title.x = element_text(colour = "#FDF202",family="OCR A Extended",face="bold"),
        axis.title.y = element_text(colour = "#FDF202",family="OCR A Extended",face="bold"),
        axis.text.x=element_text(color="White",family="OCR A Extended", face="italic"),
        axis.text.y=element_text(color="White", face="italic", family = "OCR A Extended"))
```


